---
title: "homework 9"
author: "Luke Bennett"
date: "12/9/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem 1 a)
```{r}
x = seq(1, 100)
set.seed(1)
y = 1 + 2 * x + rnorm(100, mean = 0, sd = 6) 
m <- lm(y ~ x)
summary_m <- summary(m)
beta0 <- summary_m$coefficients[1]
beta1 <- summary_m$coefficients[2]
library(ggplot2)
ggplot() + geom_point(mapping = aes(x = x, y = y)) + 
           geom_abline(slope = beta1, intercept = beta0)

```

# Problem 1 b)

\underline{Step 1} Model $$Y_i = 1 + \beta_1 * x_i + \epsilon_i, \text{where } \epsilon_i \sim N[0, 6^2]$$

\underline{Step 2} Hypotheses $$H_0: \beta_1 = 2$$
$$H_a: \beta_1 \neq 2$$

\underline{Step 3} State test statistic

Two-sided significance test

\underline{Step 4} Evaluate test stat
```{r}
df <- 99
c <- qt(0.05 / 2, df) #critical value
x_bar <- mean(x)
s_xx <- sum((x - x_bar)^2)
t <- (m$coefficients[2] - 2) / (5.416 * sqrt(1/s_xx))
```

\underline{Step 5} State Significance level $$\alpha = 0.05$$

\underline{Step 6} p-value under $H_0$
```{r}
p <- 2 * (1 - pt(abs(t), df))
```
Thus, $p = 0.866$

\underline{Step 7} Decision

Since $p = 0.886 > 0.05 = \alpha$ we accept the null hypothesis. So, $\beta_1 = 2$.

# Problem 1 c)

```{r}
beta0 <- 1:100
beta1 <- 1:100
m <- 1:100
for(i in m){
  set.seed(i)
  y = 1 + 2 * x + rnorm(100, mean = 0, sd = 6)
  l <- lm(y ~ x)
  summary_l <- summary(l)
  beta0[i] <- summary_l$coefficients[1]
  beta1[i] <- summary_l$coefficients[2]
}
df <- data.frame(beta0, beta1)
cor(df$beta0, df$beta1)
```
Correlation between beta0 hat and beta1 hat is -0.89, so they are inversely related.  
# Problem 2
```{r}
price <- c(300000, 250000, 400000, 550000, 317000, 389000, 425000, 289000, 389000)
bedrs <- c(3, 3, 4, 5, 4, 3, 6, 3, 4)
homes <- data.frame(bedrs, price)

m <- lm(price ~ bedrs, data = homes)
sum_m <- summary(m)
beta0 <- m$coefficients[1]
beta1 <- m$coefficients[2]
beta0 <- as.numeric(beta0)
beta1 <- as.numeric(beta1)
ggplot(homes) + geom_point(mapping = aes(x = bedrs, y = price)) + 
  geom_abline(slope = beta1, intercept = beta0)

predict_m <- predict(m, list(bedrs = 2:8), data = homes, interval = "confidence")
row.names(predict_m) <- 2:8
```

# Problem 3
```{r}
library(UsingR)
data(deflection)
m <- lm(Deflection ~ Load, data = deflection)
plot(m)
ggplot(data = deflection) + geom_point(mapping = aes(y = Deflection, x = Load)) +
  geom_abline(mapping = aes(slope = m$coefficients[2], intercept = m$coefficients[1]))
confint(m)
```
