---
title: "Homework 7"
author: "Luke Bennett"
date: "11/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem 1
```{r}
pnorm(170, mean = 180, sd = 25/sqrt(9))
```
Probability that the mean weight of 9 people is less than 170 lbs is 0.115
```{r}
pnorm(170, mean = 180, sd = 25)
```
Probability that a randomly selected indivudual has wt < 170 is 0.345.

# Problem 2 a)
```{r}
xbar <- 2 / 30
z <- 1.960
se <- sqrt(xbar * (1 - xbar) / 30)
lwr <- xbar - z * se
upr <- xbar + z * se
ci95 <- c(lwr, upr)
```
# Problem 2 b)
There is 95% confidence that the true mean is contained in the interval 
ci95 = (-0.0226, 0.1559).
# Problem 2 c)
```{r}
w1 <- 2 / 30
w2 <- 10 / 61
n1 <- 30
n2 <- 61
diff <- w1 - w2
se = sqrt(w1 * (1 - w1) / n1 + w2 * (1 - w2) / n2)
z <- 1.960
lwrw <- diff - z * se
uprw <- diff + z * se
ci95w <- c(lwrw, uprw)
```
confidence interval is [-0.2261, 0.0316]
# Problem 2 d
Look at the intersection ci95 and ci95w.  This is [-0.0226, 0.0316] a small interval around 0.  The first confidence interval was more to the positive end, and the confidence interval of thd difference was more negative.  This suggests w1>w2. 

# Problem 4
```{r}
library(UsingR)
data("stud.recs")
dat = stud.recs
n = nrow(dat)
xbar = mean(dat$sat.v)
se = sd(dat$sat.v) / sqrt(n) 

t = qt(1 - 0.05 / 2, df = 159) #df = n-1
lwr = xbar - t*se
upr = xbar + t*se
ci95 = c(lwr,upr)
ci95
```
Confidence interval 95% is [422, 470]