---
title: "Homework 4"
author: "Luke Bennett"
date: "10/9/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Problem 1 a)
```{r}
library(UsingR)
data("UScereal")
UScereal$mfr <- as.character(UScereal$mfr)
index_G <- which(UScereal$mfr == "G")
UScereal$mfr[index_G] <- "General Mills"
index_K <- which(UScereal$mfr == "K")
UScereal$mfr[index_K] <- "Kellogs"
index_N <- which(UScereal$mfr == "N")
UScereal$mfr[index_N] <- "Nabisco"
index_P <- which(UScereal$mfr == "P")
UScereal$mfr[index_P] <- "Post"
index_Q <- which(UScereal$mfr == "Q")
UScereal$mfr[index_Q] <- "Quaker Oats"
index_R <- which(UScereal$mfr == "R")
UScereal$mfr[index_R] <- "Ralston Purina"
UScereal$mfr <- as.factor(UScereal$mfr)
```
# Problem 1 b)
```{r}
UScereal$shelf <- factor(UScereal$shelf, levels = 1:3, labels = c("low", "medium", "high"))
```
# Problem 1 c)
```{r}
UScereal$product <- rownames(UScereal)
rownames(UScereal) <- 1:65
```
# Problem 1 str()
```{r}
print(str(UScereal))
```
# Problem 2 a)
```{r}
calpro <- cor(UScereal$cal, UScereal$protein)
calfat <- cor(UScereal$cal, UScereal$fat)
calsod <- cor(UScereal$cal, UScereal$sodium)
calfib <- cor(UScereal$cal, UScereal$fibre)
calcar <- cor(UScereal$cal, UScereal$carbo)
calsug <- cor(UScereal$cal, UScereal$sugars)
calpot <- cor(UScereal$cal, UScereal$potassium)
```
Correlations listed calories and carbos .789, fat .590, fiber .388, potassium .477, protein .706, sodium .529, sugar .495

# Problem 2 b)
```{r}
cors <- c(calpro, calfat, calsod, calfib, calcar, calsug, calpot)
names(cors) <- c("protein", "fat", "sodium", "fiber", "carbs", "sugar", "potassium")
cors <- sort(cors, decreasing = TRUE)
barplot(cors, cex.names = 0.75, 
        ylim = c(0, 1), 
        col = 1:7, ylab = "correlation", 
        main = "Cor between calories and marco/micro nutrients")
```
Carbs has the highest correlation.

# Problem 2 c) 
```{r}
plot(UScereal$calories ~ UScereal$carbo, 
     xlab = "carbs (grams)",
     ylab = "calories", 
     main = "cal ~ carbs", 
     col = "red")
lm(UScereal$calories ~ UScereal$carbo)
abline(a = 33.40, b = 5.813)
```
Y intercept is 33.40 indicated the calories in carbles cereal.  slope is how the calories change per each gram of carbs

# Problem 2 d)
```{r}
caldengm <- density(UScereal$calories[which(UScereal$mfr == "General Mills")])
caldenk <- density(UScereal$calories[which(UScereal$mfr == "Kellogs")])
xmin <- min(UScereal$calories)
xmax <- max(UScereal$calories)
ymin <- 0
plot(caldengm, xlim = c(xmin, xmax), ylim = c(0, 0.02), main = "Calorie Density", 
     xlab = "Calories")
lines(caldenk, col = "red")
legend("center", legend = c("General Mills", "Kellogs"), col = c(1, "red"),
       lty = c(1, 1), cex = 0.75)
```
These are probability functions.  
They are non-negative for all real numbers and integrate to the number 1.  
GM is distributed more heavily with lower calorie, perhaps more sugary cereal.  
Kellogs has a less extreme distibution, maybe more hearty cereal.

# Problem 2 e) 
```{r}
gm <- which(UScereal$mfr == "General Mills")
kel <- which(UScereal$mfr == "Kellogs")
boxplot(UScereal$calories[gm], UScereal$calories[kel],
        col = c("blue", "red"), 
        main = "Calorie Boxplot GM & Kel", 
        ylab = "Calories", cex.axis = 0.75, 
        names = c("General Mills", "Kellogs"))
```
GM has lower caloric yet higher spread cereal.  
Kellogs seems to have higher calorie cereal.

# Problem 2 f)
```{r}
gm <- which(UScereal$mfr == "General Mills")
k <- which(UScereal$mfr == "Kellogs")
n <- which(UScereal$mfr == "Nabisco")
p <- which(UScereal$mfr == "Post")
q <- which(UScereal$mfr == "Quaker Oats")
r <- which(UScereal$mfr == "Ralston Purina")
boxplot(UScereal$protein[gm], UScereal$protein[k], 
        UScereal$protein[n], UScereal$protein[p],  
        UScereal$protein[q], UScereal$protein[r],
        col = 2:6, main= "Protein",
        names  = c("GM", "Kellogs", "Nabisco", "Post", "QO", "Purina"),
        ylab = "grams protein")

boxplot(UScereal$fat[gm], UScereal$fat[k], UScereal$fat[n], 
        UScereal$fat[p], UScereal$fat[q], UScereal$fat[r], 
        col = 2:6, main= "Fat",
        names  = c("GM", "Kellogs", "Nabisco", "Post", "QO", "Purina"),
        ylab = "grams fat")

boxplot(UScereal$sodium[gm], UScereal$sodium[k], 
        UScereal$sodium[n], UScereal$sodium[p], 
        UScereal$sodium[q], UScereal$sodium[r], 
        col = 2:6, main= "Sodium",
        names  = c("GM", "Kellogs", "Nabisco", "Post", "QO", "Purina"),
        ylab = "milligrams sodium")

boxplot(UScereal$fibre[gm], UScereal$fibre[k], UScereal$fibre[n], 
        UScereal$fibre[p], 
        UScereal$fibre[q], UScereal$fibre[r], 
        col = 2:6, main= "Fibre",
        names  = c("GM", "Kellogs", "Nabisco", "Post", "QO", "Purina"),
        ylab = "grams fiber")

boxplot(UScereal$carbo[gm], UScereal$carbo[k], 
        UScereal$carbo[n], UScereal$carbo[p],  
        UScereal$carbo[q], UScereal$carbo[r], 
        col = 2:6, main= "carbo",
        names  = c("GM", "Kellogs", "Nabisco", "Post", "QO", "Purina"),
        ylab = "grams carbs")

boxplot(UScereal$sugars[gm], UScereal$sugars[k], 
        UScereal$sugars[n], UScereal$sugars[p],  
        UScereal$sugars[q], UScereal$sugars[r], 
        col = 2:6, main= "Sugars",
        names  = c("GM", "Kellogs", "Nabisco", "Post", "QO", "Purina"),
        ylab = "grams sugar")

boxplot(UScereal$potassium[gm], UScereal$potassium[k], 
        UScereal$potassium[n], UScereal$potassium[p],  
        UScereal$potassium[q], UScereal$potassium[r], 
        col = 2:6, main= "Potassium", 
        names  = c("GM", "Kellogs", "Nabisco", "Post", "QO", "Purina"), 
        ylab = "Milligrams K")
```
Based on these boxplot, it is clear that Nabisco has the healthiest cereal.
High fiber, protein, potassium, but low sugar and sodium.  
Average carbs and fat. 

# Problem 2 g)
```{r}
barplot(table(UScereal$mfr, UScereal$shelf), 
        col = c("blue", "darkred", "black", "red", "darkblue", "white"),
        ylim = c(0, 40),
        main = "shelf location of brands"
        )
legend("topleft", 
       legend = c("General Mills", "Kellogs", "Nabisco", "Post", 
                        "Quaker Oats", "Ralston Purina"), 
       fill = c("blue", "darkred", "black", "red", "darkblue", "white"), 
       cex = 0.65)
```